---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dev = "png",
  dpi = 150,
  fig.asp = 0.8,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center"
)
```

# posterior

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/posterior)](https://CRAN.R-project.org/package=posterior)
[![Travis Build Status](https://travis-ci.org/stan-dev/posterior.svg?branch=master)](https://travis-ci.org/stan-dev/posterior)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/stan-dev/posterior?branch=master&svg=true)](https://ci.appveyor.com/project/jgabry/posterior)
[![Coverage Status](https://codecov.io/gh/stan-dev/posterior/branch/master/graph/badge.svg)](https://codecov.io/gh/stan-dev/posterior)
<!-- badges: end -->


The **posterior** R package is intended to provide useful tools for both users
and developers of packages for fitting Bayesian models or working with output
from Bayesian models. The primary goals of the package are to:

* Efficiently convert between many different useful formats of
  draws (samples) from posterior or prior distributions.
* Provide various summaries of draws in convenient formats.
* Provide lightweight implementations of state of the art MCMC diagnostics.

### Installation

The package is not released yet. Currently you can install the development
version from GitHub, but expect frequent changes until an official release.

```{r install, eval=FALSE}
# install.packages("remotes")
remotes::install_github("stan-dev/posterior")
```

### Examples

```{r load}
library("posterior")
```

To demonstrate how to work with the **posterior** package, we will use example
posterior draws obtained from the eight schools hierarchical meta-analysis model
described in Gelman et al. (2013). Essentially, we have an estimate per school
(`theta[1]` through `theta[8]`) as well as an overall mean (`mu`) and standard
deviation across schools (`tau`).

#### Draws formats 

```{r draws_array}
eight_schools_array <- example_draws("eight_schools")
print(eight_schools_array, max_variables = 3)
```

The draws for this example come as a `draws_array` object, that is, an array
with dimensions iterations x chains x variables. We can easily transform it to
another format, for instance, a data frame with additional meta information.

```{r draws_df}
eight_schools_df <- as_draws_df(eight_schools_array)
print(eight_schools_df)
```

Different formats are preferable in different situations and hence posterior
supports multiple formats and easy conversion between them. For more details on
the available formats see `help("draws")`. All of the formats are essentially
base R object classes and can be used as such. For example, a `draws_matrix`
object is just a `matrix` with a little more consistency and additional methods.

#### Draws summaries

Computing summaries of posterior or prior draws and convergence diagnostics for
posterior draws is one of the most common tasks when working with Bayesian
models fit using Markov Chain Monte Carlo (MCMC) methods. The **posterior**
package provides a flexible interface for this purpose via `summarise_draws()`:

```{r summary}
# summarise_draws or summarize_draws
summarise_draws(eight_schools_df)
```

Basically, we get a data frame with one row per variable and one column per
summary statistic or convergence diagnostic. We can choose which summaries to
compute by passing additional arguments, either functions or names of functions.
For instance, if we only wanted the mean and its corresponding Monte Carlo
Standard Error (MCSE) we would use:

```{r summary-with-measures}
summarise_draws(eight_schools_df, "mean", "mcse_mean")
```

For a function to work with `summarise_draws`, it needs to take a vector or
matrix of numeric values and returns a single numeric value or a named vector of
numeric values.

#### Subsetting draws 

Another common task when working with posterior (or prior) draws, is subsetting
according to various aspects of the draws (iterations, chains, or variables).
**posterior** provides a convienent interface for this purpose via the
`subset()` method. For example, here is the code to extract the first five 
iterations of the first two chains of the variable `mu`:

```{r subset}
subset_draws(eight_schools_df, variable = "mu", chain = 1:2, iteration = 1:5)
```

The same call to `subset_draws()` can be used regardless of whether the object 
is a `draws_df`, `draws_array`, `draws_list`, etc.

#### Converting from regular R objects to draws formats

The `eight_schools` example already comes in a format natively supported by
posterior but we could of course also import the draws from other sources,
for example, from common base R objects:

```{r draws_matrix}
x <- matrix(rnorm(50), nrow = 10, ncol = 5)
colnames(x) <- paste0("V", 1:5)
x <- as_draws_matrix(x)
print(x)

summarise_draws(x, "mean", "sd", "median", "mad")
```

Instead of `as_draws_matrix()` we also could have just used `as_draws()`, which
attempts to find the closest available format to the input object. In this case
this would result in a `draws_matrix` object either way.

### Contributing

We welcome contributions! The **posterior** package is under active development.
If you find bugs or have ideas for new features (for us or yourself to
implement) please open an issue on GitHub
(https://github.com/stan-dev/posterior/issues).

### References

Andrew Gelman, John B. Carlin, Hal S. Stern, David B. Dunson, Aki Vehtari and
Donald B. Rubin (2013). Bayesian Data Analysis, Third Edition. Chapman and
Hall/CRC.
