---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dev = "png",
  dpi = 150,
  fig.asp = 0.8,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center"
)
```

# posterior

<!-- badges: start -->
[![Build Status](https://travis-ci.org/jgabry/posterior.svg?branch=master)](https://travis-ci.org/jgabry/posterior)
[![Coverage Status](https://codecov.io/github/jgabry/posterior/coverage.svg?branch=master)](https://codecov.io/github/jgabry/posterior?branch=master)
<!-- badges: end -->

## Overview

The **posterior** R package is intended to provide useful tools for both users
and developers of packages for fitting Bayesian models or working with output
from Bayesian models. The primary goals of the package are to:

* Efficiently convert between many different useful formats of
  draws (samples) from posterior or prior distributions.
* Provide various summaries of draws in convenient formats.
* Provide lightweight implementations of state of the art MCMC diagnostics.

## How to use posterior

```{r}
library(posterior)
```

To demonstrate how to work with the posterior package, we will apply it to
posterior draws obtained from the eight schools model described in Gelman et al.
(2013). Essentially, we have an estimate per school (variables `theta[1]` to
`theta[8]`) as well as an overall mean and standard deviation across schools
(variables `mu` and `tau`, respectively).

```{r}
eight_schools <- example_draws("eight_schools")
```

The draws for this example come as a `draws_array` object, that is, an array
with dimensions iterations x chains x variables. We can easily transform it to
another format, for instance, data frame with additional meta information.

```{r}
eight_schools <- as_draws_df(eight_schools)
print(eight_schools)
```

Different formats are preferable in different situations and hence posterior
supports multiple formats and easy conversion between them. For more details see
`help("draws")`.

Summarising posterior draws and computing convergnece diagnostics is one of the
most common tasks when working with Markov Chain Monte Carlo (MCMC) draws. The
posterior package provides a flexible interface for thus purpose with sensible
defaults.

```{r}
summarise_draws(eight_schools)
```

Basically, we get a data frame one row per variable and one column summary
statistics or convergence diagnostics. We can choose which summaries to compute
via the `measures` argument. For instance, if we were just interested in the
mean and corresponding Monto Carlo Standard Error (MCSE), we could write

```{r}
summarise_draws(eight_schools, measures = c("mean", "mcse_mean"))
```

For a measure to work, there needs to be a function defined with the same
name as specified in `measures` which takes a vector or matrix of numeric
values and returns a single numeric value or a named vector of numeric values.

Another common task when working with posterior (or prior) draws, is subsetting
various aspects of the draws, that is, iterations, chains, or variables.
posterior provides a convienent interface for this purpose via the `subset` 
method. For instance, if we want to extract the first 5 iterations
of the first two chains of the variables `mu`, we can write

```{r}
mu <- subset(eight_schools, variable = "mu", chain = 1:2, iteration = 1:5)
mu
```

The `eight_schools` example already comes in a format natively supported by
posterior but we could of course also import the draws from other sources,
for example, from common base R objects.

```{r}
x <- matrix(rnorm(50), nrow = 10, ncol = 5)
colnames(x) <- paste0("V", 1:5)
x <- as_draws_matrix(x)
head(x)
```

The posterior is under active development. If you find bugs or have ideas for
new features, you are very welcome to open an issue on GitHub
(https://github.com/jgabry/posterior).

## Installation

The package is not released yet. Currently you can install the development
version from GitHub, but expect frequent changes until an official release.

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("jgabry/posterior")
```

## References

Andrew Gelman, John B. Carlin, Hal S. Stern, David B. Dunson, Aki Vehtari and Donald B. Rubin (2013). Bayesian Data Analysis, Third Edition. Chapman and Hall/CRC.

Aki Vehtari, Andrew Gelman, Daniel Simpson, Bob Carpenter, and Paul-Christian Bürkner (2019). Rank-normalization, folding, and localization: An improved R-hat for assessing convergence of MCMC. arXiv preprint arXiv:1903.08008.
